---
title: "Homework 3 Classification"
author: "Jinfei Xue"
date: "2/6/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 4.6

## (a)

*We can obtain the logistic regression:*

$$logit(p)=-6+0.05X_1+X_2$$

```{r}
library(boot)
inv.logit(-6+0.05*40+3.5)
```

*So the estimated probability that a student who studies for 40 h and has an undergrad GPA of 3.5 gets an A in the class is 0.3775407.*

## (b)

```{r}
(logit(0.5)-(-6)-3.5)/0.05
```

*So the student in part (a) need to study 50 hours to have a 50% chance of getting an A in the class.*

# 4.8


# 4.9

## (a) 

*We can obtain:*

$$\frac{p}{1-p}=0.37$$

*We can transform it into:*

$$p=\frac{0.37}{1+0.37}\approx0.27$$

*So, on average, 27% of people with an odds of 0.37 of defaulting on their credit card payment will in fact default.*

## (b)

*The odds that she will default is:*

$$\frac{p}{1-p}=\frac{0.16}{1-0.16}\approx0.19$$

# 4.10

## (a)

```{r}
library(ISLR)
data(Weekly)
Weekly = Weekly

# numerical summary
summary(Weekly)

# graphical summary
library(ggplot2)
index=1:length(Weekly$Volume)
ggplot(Weekly) + geom_point(aes(x=index,y=Volume))

```

*When we plot “Volume”, we can see that it is increasing over time.*

## (b)

```{r}
r10_b <- glm(Direction ~ Lag1 + Lag2 + Lag3 + Lag4 + Lag5 + Volume, 
               data = Weekly, family = binomial)
summary(r10_b)
```

*It would seem that "Lag2"" is the only predictor statistically significant as its p-value is less than 0.05.*
















